Principles for Open Data Curation: A Case Study with the New York City 311 Service Request Data

### 2024-11-07 manuscript/manuscript.tex
Further edting
Added enumitem package and idented itemized lists. Rearranged a couple of paragraphs for better organization. Cosmetic changes to standardize presentation and improve readability.

\usepackage{comment}
\usepackage{booktabs, textgreek}
\usepackage{subcaption}

@@

Our investigation utilizes an SR dataset covering  2\mbox{-}years (2022-2023).
This dataset is approximately 3.7 GB in size and contains over 
6.4 million rows with each row representing one SR. It contains 
41 columns of data and was collected on 15 September 2023. The 
dataset is used to conduct detailed analysis 
in areas such as data consistency, data validity, redundant fields, 
etc.. Instructions on downloading this file from the 
NYC Open Data Portal are available in the supplemental material.

\begin{itemize}
    \item New York Police Department (NYPD) - 43\% of all SRs
    \item Housing Preservation and Development (HPD) - 21\%
    \item New York City Department of Sanitation (DSNY) - 10\%
    \item Department of Transportation (DOT) - 7\%
    \item Department of Environmental Protection (DEP) - 5\%
    \item Department of Parks and Recreation (DPR) - 4\%
\end{itemize}

\section{NYC 311 SR Data Cleansing Issues} 
\label{sec:issues}
Data cleansing refers to the process of identifying and rectifying
errors, inconsistencies, and inaccuracies within datasets to ensure
they are of high quality and reliable for analysis
\citep{maletic2005data, hosseinzadeh2023data}. The process
typically involves removing duplicate records, handling missing or
incomplete data, correcting mislabeled or inaccurate entries, and
standardizing data formats \citep[e.g.,][]{cody2017cody,
  van2018statistical}. In the context of open data, cleansing is
especially important as open datasets often come from diverse,
often uncoordinated sources, leading to variations in data quality,
completeness, and consistency. Without thorough data cleansing, 
the utility of open data can be limited and perhaps 
untrustworthy, affecting its reliability for research, 
policy making, and innovation. The main purpose of cleansing 
open data is to ensure that it is accurate, consistent, and usable a
cross multiple analytical platforms and by various stakeholders with a 
myriad of purposes. Data cleansing improves the trustworthiness 
of the data and enables more accurate analysis, 
better decision making, and the improved integration of 
data into machine learning models or other systems.

Many quality criteria are employed to ensure high\mbox{-}quality data 
processing. One of the primary efforts is data validation, which spans 
several critical checks. For instance, mandatory fields must not be 
left empty, ensuring that key information is always captured. 
Additionally, certain fields must conform to specific data types, 
such as numeric, character, or date formats; typically 
outlined in a \href{https://data.cityofnewyork.us/api/views/erm2-nwe9/files/b372b884-f86a-453b-ba16-1fe06ce9d212?download=true&filename=311_ServiceRequest_2010-Present_DataDictionary_Updated_2023.xlsx}{Data Dictionary}. An 
essential aspect of validation 
is domain compliance, where fields must adhere to a predefined set of 
values such as statuses, state names, or zip codes. Structural 
errors can also play a significant role in data quality, particularly when 
naming conventions or data entries are inconsistent. Common issues 
include fields that do not appear in the Data Dictionary 
and the inconsistent use of blanks, spaces, NA, N/A, 
or ``<NA>'' to indicate missing data. Furthermore, redundant 
or irrelevant fields can clutter datasets, reducing efficiency and 
creating confusion or errors. Logical inconsistencies are another 
consideration, such as related fields that violate expected 
relationships, e.g. a ``due date'' that precedes the ``created date.'' 
Lastly, the balance between accuracy and precision is crucial, as both 
must be carefully managed to ensure meaningful data.

Here we identify the presence of issues in the NYC 311 SR open dataset;
not attempting to solve them, but rather to highlight their scope and
magnitude. We would recommend that a solution effort 
should be undertaken only after further investigation as to 
the why and how such issues came about, including a
discussion as to whether or not it is an actual \textit{error} or 
holds some other status. Coordination with the originating Agency
is, of course, paramount.

\subsection{Structural Issues}
\label{sec:structural}
Structural issues refers to how data is organized, formatted, 
or presented within a dataset. Structural issues can make 
it difficult to analyze the data effectively. Here are some overall 
characteristics of the 311 SR data set:

\begin{itemize}
	\item There are 41 columns of data for each row, exportable as a CSV file.
	Each row represents a single Service Request (SR).

@@

The 311 SR 
\href{https://data.cityofnewyork.us/api/views/erm2-nwe9/files/b372b884-f86a-453b-ba16-1fe06ce9d212?download=true&filename=311_ServiceRequest_2010-Present_DataDictionary_Updated_2023.xlsx}{Data Dictionary} 
identifies 41 data columns (fields) and provides related information 
for each. However, there are six additional fields that can be
optionally downloaded. These fields are 
visible in the portal's ``Column manager'' widget, labeled with the prefix 
``@computed\_region.'' and include:

\begin{itemize}
    \item \texttt{zip\_codes}
    \item \texttt{community\_districts}
    \item \texttt{borough\_boundaries}
    \item \texttt{city\_council\_districts}
    \item \texttt{police\_precincts}
    \item \texttt{police\_precinct}
\end{itemize}

While one can likely infer the meaning of these ``computed'' 
fields, uncertainty remains as to their derivation and 
usage. These six fields are not included in
the \href{https://data.cityofnewyork.us/api/views/erm2-nwe9/files/b372b884-f86a-453b-ba16-1fe06ce9d212?download=true&filename=311_ServiceRequest_2010-Present_DataDictionary_Updated_2023.xlsx}{Data Dictionary}. Our 
analysis shows that these six ``computed'' fields have 
significant data validity issues, leading us to treat these six fields 
as experimental and not for suitable for normal use. Accordingly, 
we will not address these fields in our analysis.

\subsection{Missing Data}
\label{sec:blanks}
Understanding the absence of data by field is important 
when undertaking analysis. For example, if you wanted to 
determine if SRs were closed before or after their
\texttt{due\_date}, you would be challenged as 99.6\% of the
\texttt{due\_date} fields are blank. When sorting fields by
blank or N/A values, they appear to divide into three groups:

\begin{itemize}
    \item \textbf{Mostly Empty} -- 93-99.9\% blank 
    \item \textbf{Partially Empty} -- 40-4\% blank
    \item \textbf{Few/None Empty} -- 2-0\% blank
\end{itemize}

The Mostly Empty category includes such fields as
\texttt{taxi\_company\_borough}, \texttt{due\_date},
\texttt{road\_ramp}, and \texttt{bridge\_highway\_name}.
The Partially Empty category includes such fields as
\texttt{location\_type}, \texttt{landmark}, 
and \texttt{cross\_street\_1 \& \_2}. And the Few/None Empty category
 includes \texttt{created\_date}, \texttt{complaint\_type},
\texttt{agency}, and \texttt{status}. For some analysis efforts, it may be
prudent to inquire as to why some fields are mostly or almost always blank.
Figure~\ref{fig:blank_fields} presents a graphic 
depiction of total empty (blank \& N/As) for each fields illustrating
the grouping into the Most, Partial, and Few categories.

@@

\begin{itemize}
    \item \texttt{address\_type}
    \item \texttt{status}
    \item \texttt{borough}
    \item \texttt{borough\_boundaries}
    \item \texttt{park\_borough}
    \item \texttt{data\_channel}
    \item \texttt{vehicle\_type}
    \item \texttt{city\_council\_district}
\end{itemize}

@@

\begin{itemize}
    \item SRs with a \texttt{closed\_date} that occurs before the 
    \texttt{created\_date} resulting a nonsensical ``negative duration''.
    \item \texttt{created\_date(s)} and \texttt{closed\_date(s)} in 
    the far distant past, e.g. ``1900-01-01''.
    \item \texttt{created\_date(s)} and \texttt{closed\_date(s)} that 
    match \textbf{to the second} creating an impossible ``zero duration''.
    \item An unusually large number of SRs closed and/or created exactly at midnight 
    and noon, to the second.
\end{itemize}

@@

\paragraph{\texttt{Latitude/Longitude} and \texttt{location}}: 
The \texttt{location} field is a pure concatenation of 
the \texttt{latitude} and \texttt{longitude} fields albeit with a 
comma and parentheses added. This makes the \texttt{location} field 
arguably harder to use than the individual fields. For example:  
\texttt{latitude}: 40.768456429488, \texttt{longitude}: $-$73.9575661888774, 
form the \texttt{location}: (40.768456429488, $-$73.95756618887745).

\paragraph{\texttt{borough} \& \texttt{park\_borough}}: These two fields are fully redundant, 
as they are 100\% matches.

\paragraph{\texttt{borough} \& \texttt{taxi\_company\_borough}}: Despite 
their names, these fields are almost entirely different, with only 
a 0.05\% match. The \texttt{taxi\_company\_borough} field is 
used exclusively by the TLC, indicating a need for consultation 
with that Agency to understand the differing uses. It is 
likely that that the usage of \texttt{taxi\_company\_borough} is 
quite different than that of \texttt{borough}.

\paragraph{\texttt{agency} \& \texttt{agency\_name}}: The \texttt{agency} 
field contains the abbreviations of City agencies (e.g., NYPD, DOT, DSNY), 
while \texttt{agency\_name} contains the full names. Including both seems 
redundant, especially given the space taken up by full names in the 
CSV file. Additionally, the Agency abbreviations are easily recognized.

\paragraph{\texttt{landmark} \& \texttt{street\_name}}: Per the \href{https://data.cityofnewyork.us/api/views/erm2-nwe9/files/b372b884-f86a-453b-ba16-1fe06ce9d212?download=true&filename=311_ServiceRequest_2010-Present_DataDictionary_Updated_2023.xlsx}{Data Dictionary}, the \texttt{landmark} field ``can refer to any 
noteworthy location, including but not limited to, parks, 
hospitals, airports, sports facilities, performance spaces, etc.'  
However, most entries are actually street names, with a 62\% 
match to \texttt{street\_name} field. Even the non\mbox{-}matches (excluding 
blanks) appear to be a logical match, differing only in spelling or formatting 
(e.g., ``NINTH AVE'' vs. ``9 AVE''). This indicates a possible 
misuse of the \texttt{landmark} field as well as a high level of redundancy.

\paragraph{\texttt{cross\_street\_1/2} \& \texttt{intersection\_street\_1/2}}: These 
two sets of street pairs are used to help identify the 
\texttt{incident address}. We found 88\% of both of these two 
street pairs to be duplicates. Such a high leve of duplication 
raises the question of which field\mbox{-}pair should be trusted; 
and if these street pairs are used differently, how should they be treated?
It is possible that these two street pairs originated from different 
agencies that use different variable names to represent the same 
information, but no documentation exists to clarify this 
relationship. These two street\mbox{-}pairs are highly redundant.

\subsection{Storage}
\label{sec:filesize}
By removing duplicate and ``near\mbox{-}duplicate'' fields, it is possible to 
shrink the file size by 39.5\%, which for this large dataset equates to 
a reduction of 1.4GB, a significant amount. A smaller file size 
means faster downloads, less storage impact, and often 
simpler data analysis efforts. Below is a list of duplicate 
and near\mbox{-}duplicate fields which we believe could be
removed from the dataset with minimal data loss.

\begin{itemize}
    \item \textbf{\texttt{agency\_name}}: Since each row contains the \texttt{agency} 
    field, which uses clear and well understood abbreviations, we believe the
    \texttt{agency\_name} can be removed with minimal data loss.

@@

\begin{quote}
\textbf{Note:} \textit{Even a field that is 99\% blank still contains 64,000 
non\mbox{-}blank rows in this large (6.4 million row) 
dataset.} Non\mbox{-}trivial.
\end{quote}

\begin{itemize}
    \item \texttt{taxi\_company\_borough}
    \item \texttt{road\_ramp}
    \item \texttt{vehicle\_type}
    \item \texttt{due\_date}
    \item \texttt{bridge\_highway\_direction}
    \item \texttt{bridge\_highway\_name}
    \item \texttt{bridge\_highway\_segment}
    \item \texttt{taxi\_pick\_up\_location}
\end{itemize}

@@

\begin{itemize}
    \item While the NYC Open Data portal lists the data types of various 
    fields, the \href{https://data.cityofnewyork.us/api/views/erm2-nwe9/files/b372b884-f86a-453b-ba16-1fe06ce9d212?download=true&filename=311_ServiceRequest_2010-Present_DataDictionary_Updated_2023.xlsx}{Data Dictionary} does not. Nor does it provide details for specific fields such as constraints or the domain of legal 
    values. For example, in the \href{https://data.cityofnewyork.us/api/views/erm2-nwe9/files/b372b884-f86a-453b-ba16-1fe06ce9d212?download=true&filename=311_ServiceRequest_2010-Present_DataDictionary_Updated_2023.xlsx}{Data Dictionary}, the \texttt{incident\_zip} 
    field is specified as ``text.'' This may not be the most suitable 
    definition. Perhaps ``categorical,'' with a note indicating that 
    the data must contain only numeric values and is not subjected to 
    arithmetic operations would be a better dictionary description.

>>>>

\usepackage{comment}
\usepackage{booktabs, textgreek}
\usepackage{subcaption}
\usepackage{enumitem}

@@

Our investigation utilizes an SR dataset covering  2\mbox{-}years (2022-2023).
This dataset is approximately 3.7 GB in size and contains over 
6.4 million rows with each row representing one SR. It contains 
41 columns of data and was collected on 15 September 2023. The 
dataset is used to conduct detailed analysis 
in areas such as data consistency, data validity, redundant fields, 
etc.. Instructions on downloading this file from the 
NYC Open Data Portal are available in the supplemental material.
Here are some characteristics of the 311 SR data set:

\begin{itemize}[left=1.5em]
	\item There are 41 columns of data for each row, exportable as a CSV file.
	Each row represents a single Service Request (SR).

@@

\begin{itemize}[left=1.5em]
    \item New York Police Department (NYPD): 43\% of all SRs
    \item Housing Preservation and Development (HPD): 21\%
    \item New York City Department of Sanitation (DSNY): 10\%
    \item Department of Transportation (DOT): 7\%
    \item Department of Environmental Protection (DEP): 5\%
    \item Department of Parks and Recreation (DPR): 4\%
\end{itemize}

\section{Data Cleansing Issues} 
\label{sec:issues}
Data cleansing refers to the process of identifying and rectifying
errors, inconsistencies, and inaccuracies within datasets to ensure
they are of high quality and reliable for analysis
\citep{maletic2005data, hosseinzadeh2023data}. The process
typically involves removing duplicate records, handling missing or
incomplete data, correcting mislabeled or inaccurate entries, and
standardizing data formats \citep[e.g.,][]{cody2017cody,
  van2018statistical}. In the context of open data, cleansing is
especially important as open datasets often come from diverse,
often uncoordinated sources, leading to variations in data quality,
completeness, and consistency. Without thorough data cleansing, 
the utility of open data can be limited and perhaps 
untrustworthy, affecting its reliability for research, 
policy making, and innovation. The main purpose of cleansing 
open data is to ensure that it is accurate, consistent, and usable a
cross multiple analytical platforms and by various stakeholders with a 
myriad of purposes. Data cleansing improves the trustworthiness 
of the data and enables more accurate analysis, 
better decision making, and the improved integration of 
data into machine learning models or other systems.

Many quality criteria are employed to ensure high\mbox{-}quality data 
processing. One of the primary efforts is data validation, which spans 
several critical checks. For instance, mandatory fields must not be 
left empty, ensuring that key information is always captured. 
Additionally, certain fields must conform to specific data types, 
such as numeric, character, or date formats; typically 
outlined in a \href{https://data.cityofnewyork.us/api/views/erm2-nwe9/files/b372b884-f86a-453b-ba16-1fe06ce9d212?download=true&filename=311_ServiceRequest_2010-Present_DataDictionary_Updated_2023.xlsx}{Data Dictionary}. An 
essential aspect of validation is domain compliance, where 
fields must adhere to a predefined set of 
values such as statuses, state names, or zip codes. Structural 
errors can also play a significant role in data quality, particularly when 
naming conventions or data entries are inconsistent. Common issues 
include fields that do not appear in the Data Dictionary,  
inconsistent use of data fields. Furthermore, redundant 
or irrelevant fields can clutter datasets, reducing efficiency, 
creating confusion, and introducing errors. Logical inconsistencies 
are another consideration, such as related fields that violate expected 
relationships, e.g. a ``due date'' that precedes the ``created date.'' 
Lastly, the balance between accuracy and precision is crucial, as both 
must be carefully managed to ensure meaningful data.

We identify the presence of issues in the NYC 311 SR open dataset;
not attempting to solve them, but rather to highlight their scope, 
magnitude, and potential impact. We would recommend 
that a corrective solution should be undertaken only 
after further investigation as to the why and how such 
issues might come about, including  detailed discussions 
with the originating Agency as to whether or not it is an 
actual error, correct,  or holds some other status.

\subsection{Structural Issues}
\label{sec:structural}
Structural issues refers to how data is organized, formatted, 
or presented within a dataset. They can make 
it difficult to analyze the data effectively and often require extensive 
data cleaning efforts. Here are three structural issues we encountered.

\paragraph{Undocumented Fields:} The 311 SR 
\href{https://data.cityofnewyork.us/api/views/erm2-nwe9/files/b372b884-f86a-453b-ba16-1fe06ce9d212?download=true&filename=311_ServiceRequest_2010-Present_DataDictionary_Updated_2023.xlsx}{Data Dictionary} 
identifies 41 data columns (fields) and provides related information 
for each. However, there are six additional fields that can be
optionally downloaded. These fields are 
visible in the portal's ``Column manager'' widget, labeled with the prefix 
``@computed\_region.'' and include:

\begin{itemize}[left=1.5em]
    \item \texttt{zip\_codes}
    \item \texttt{community\_districts}
    \item \texttt{borough\_boundaries}
    \item \texttt{city\_council\_districts}
    \item \texttt{police\_precincts}
    \item \texttt{police\_precinct}
\end{itemize}

While one can likely infer the meaning of these ``computed'' 
fields, uncertainty remains as to their derivation and 
usage. These six fields are not included in
the \href{https://data.cityofnewyork.us/api/views/erm2-nwe9/files/b372b884-f86a-453b-ba16-1fe06ce9d212?download=true&filename=311_ServiceRequest_2010-Present_DataDictionary_Updated_2023.xlsx}{Data Dictionary}. Additionally, 
our analysis shows that these six ``computed'' fields have 
significant data validity issues, leading us to treat these six fields 
as experimental and \textit{not for suitable for public use}. An update 
to the Data Dictionary would seem appropriate. Accordingly, 
we will not address these fields in our analysis.

\paragraph{Representation of Missing data:} We found that the 
311 SR dataset exhibited inconsistent approaches when 
presenting missing data. We discovered many different 
representations of missing data: nulls, spaces, ``NA'', ``N/A'', 
and ``<NA>''. This variety of representations complicates programming
efforts, and increases the likelihood of introducing errors 
in data analysis (typically by search for or excluding missing fields 
and not aware of the various representations). A more consistent 
approach to treating missing data should be employed to address this issue.

\paragraph{Challenges with daylight saving time (DST):} The 311 SR 
dataset captures local NYC times. Accordingly, twice each 
year there are changes to the local time as a result of observing 
DST, and this can introduce some unexpected results. For example, 
on March 13, 2022 and March 12, 2023 there are no times 
between 1:59AM and 2:59AM: the 2:00AM hour on those dates 
is simply missing owing to the clocks moving forward; at 2:00AM 
it instantly becomes 3:00AM. This creates a gap in the hourly 
distribution of SRs on those days, and it exaggerates the 
lifespan of SRs, albeit by a single hour. Similarly on 
November 6, 2022 and November 5, 2023, the 
hour of 1:00AM - 2:00AM is repeated twice. This can result 
in a bizarre scenario where, for example, an SR can 
be created at 1:59AM and then closed say 30 minutes later 
at 1:29AM; seemingly nonsensical. Utilizing UTC time 
for date\mbox{-}time stamps might help address this issue.

\subsection{Missing Data by Field}
\label{sec:blanks}
Understanding the absence of data by field is important 
when undertaking analysis. For example, if you wanted to 
determine if SRs were closed before or after their
\texttt{due\_date}, you would be challenged as 99.6\% of the
\texttt{due\_date} field are blank. When sorting fields by
blank (or N/A values) they appear to divide into three groups:

\begin{itemize}[left=1.5em]
    \item \textbf{Mostly Empty}: 93-99.9\% blank 
    \item \textbf{Partially Empty}: 40-4\% blank
    \item \textbf{Few/None Empty}: 2-0\% blank
\end{itemize}

The \textit{Mostly Empty} category includes fields such as
\texttt{taxi\_company\_borough}, \texttt{due\_date},
\texttt{road\_ramp}, and \texttt{bridge\_highway\_name}.
The \textit{Partially Empty} category includes fields such as
\texttt{location\_type}, \texttt{landmark}, 
and \texttt{cross\_street\_1 \& \_2}. And the \textit{Few/None Empty} 
category includes \texttt{created\_date}, \texttt{complaint\_type},
\texttt{agency}, and \texttt{status}. For some analysis efforts, it may be
prudent to inquire further as to why some fields are 
mostly or almost always blank. Figure~\ref{fig:blank_fields} is 
a graphic depiction of total empty (blank \& N/As) for each field illustrating
the grouping into the Most, Partial, and Few categories.

@@

\begin{itemize}[left=1.5em]
    \item \texttt{address\_type}
    \item \texttt{status}
    \item \texttt{borough}
    \item \texttt{borough\_boundaries}
    \item \texttt{park\_borough}
    \item \texttt{data\_channel}
    \item \texttt{vehicle\_type}
    \item \texttt{city\_council\_district}
\end{itemize}

@@

\begin{itemize}[left=1.5em]
    \item SRs with a \texttt{closed\_date} that occurs before the 
    \texttt{created\_date} resulting a nonsensical ``negative duration''.
    \item \texttt{created\_date(s)} and \texttt{closed\_date(s)} in 
    the far distant past, e.g. ``1900-01-01''.
    \item \texttt{created\_date(s)} and \texttt{closed\_date(s)} that 
    match \textbf{to the second} creating an impossible ``zero duration''.
    \item An unusually large number of SRs closed and/or created exactly at midnight 
    and noon, to the second.
\end{itemize}

@@

\paragraph{\texttt{latitude/longitude} \& \texttt{location}:} 
The \texttt{location} field is a pure concatenation of 
the \texttt{latitude} and \texttt{longitude} fields albeit with a 
comma and parentheses added. This makes the \texttt{location} field 
arguably harder to use than the individual fields. For example:  
\texttt{latitude}: 40.768456429488, \texttt{longitude}: $-$73.9575661888774, 
form the \texttt{location}: (40.768456429488, $-$73.95756618887745).

\paragraph{\texttt{borough} \& \texttt{park\_borough}:} These two fields are fully redundant, 
as they are 100\% matches.

\paragraph{\texttt{borough} \& \texttt{taxi\_company\_borough}:} Despite 
their names, these fields are almost entirely different, with only 
a 0.05\% match. The \texttt{taxi\_company\_borough} field is 
used exclusively by the TLC, indicating a need for consultation 
with that Agency to understand the differing uses. It is 
likely that that the usage of \texttt{taxi\_company\_borough} is 
quite different than that of \texttt{borough}.

\paragraph{\texttt{agency} \& \texttt{agency\_name}:} The \texttt{agency} 
field contains the abbreviations of City agencies (e.g., NYPD, DOT, DSNY), 
while \texttt{agency\_name} contains the full names. Including both seems 
redundant, especially given the space taken up by full names in the 
CSV file. Additionally, the Agency abbreviations are easily recognized.

\paragraph{\texttt{landmark} \& \texttt{street\_name}:} Per the \href{https://data.cityofnewyork.us/api/views/erm2-nwe9/files/b372b884-f86a-453b-ba16-1fe06ce9d212?download=true&filename=311_ServiceRequest_2010-Present_DataDictionary_Updated_2023.xlsx}{Data Dictionary}, 
the \texttt{landmark} field ``can refer to any noteworthy location, 
including but not limited to, parks, hospitals, airports, sports facilities, 
performance spaces, etc.'. However, most entries are actually 
street names, with a 62\% match to \texttt{street\_name} field. 
Even the non\mbox{-}matches (excluding blanks) appear to be 
a logical match, differing only in spelling or formatting 
(e.g., ``NINTH AVE'' vs. ``9 AVE''). This indicates a possible 
misuse of the \texttt{landmark} field as well as a high level of redundancy.

\paragraph{\texttt{cross\_street\_1/2} \& \texttt{intersection\_street\_1/2}:} These 
two sets of street pairs are used to help identify the 
\texttt{incident address}. We found 88\% of both of these two 
street pairs to be duplicates. Such a high level of duplication 
raises the question of which field\mbox{-}pair should be trusted; 
and if these street pairs are used differently, how should they be treated?
It is possible that these two street pairs originated from different 
agencies that use different variable names to represent the same 
information, but no documentation exists to clarify this 
relationship. These two street\mbox{-}pairs are highly redundant.

\subsection{Reducing File Size}
\label{sec:filesize}
By removing duplicate and ``near\mbox{-}duplicate'' fields, it is possible to 
shrink the file size by 39.5\%, which for this large dataset equates to 
a reduction of 1.4GB, a significant amount. A smaller file size 
means faster downloads, less storage impact, and often 
simpler data analysis efforts. Below is a list of duplicate 
and near\mbox{-}duplicate fields which we believe could be
removed from the dataset with minimal data loss.

\begin{itemize}[left=1.5em]
    \item \textbf{\texttt{agency\_name}}: Since each row contains the \texttt{agency} 
    field, which uses clear and well understood abbreviations, we believe the
    \texttt{agency\_name} can be removed with minimal data loss.

@@

\begin{quote}
\textbf{Note:} \textit{Even a field that is 99\% blank will contain 64,000 
non\mbox{-}blank rows in this large (6.4 million row) 
dataset.} Non\mbox{-}trivial.
\end{quote}

\begin{itemize}[left=1.5em]
    \item \texttt{taxi\_company\_borough}
    \item \texttt{road\_ramp}
    \item \texttt{vehicle\_type}
    \item \texttt{due\_date}
    \item \texttt{bridge\_highway\_direction}
    \item \texttt{bridge\_highway\_name}
    \item \texttt{bridge\_highway\_segment}
    \item \texttt{taxi\_pick\_up\_location}
\end{itemize}

@@

\begin{itemize}[left=1.5em]
    \item While the NYC Open Data portal lists the data types of various 
    fields, the \href{https://data.cityofnewyork.us/api/views/erm2-nwe9/files/b372b884-f86a-453b-ba16-1fe06ce9d212?download=true&filename=311_ServiceRequest_2010-Present_DataDictionary_Updated_2023.xlsx}{Data Dictionary} does not. Nor does it provide details for specific fields such as constraints or the domain of legal 
    values. For example, in the \href{https://data.cityofnewyork.us/api/views/erm2-nwe9/files/b372b884-f86a-453b-ba16-1fe06ce9d212?download=true&filename=311_ServiceRequest_2010-Present_DataDictionary_Updated_2023.xlsx}{Data Dictionary}, the \texttt{incident\_zip} 
    field is specified as ``text.'' This may not be the most suitable 
    definition. Perhaps ``categorical,'' with a note indicating that 
    the data must contain only numeric values and is not subjected to 
    arithmetic operations would be a better dictionary description.
